---
title: "Financial Big Data Quiz 3"
author: "108070014  陳品妤"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    number_sections: false
---

<style type = "text/css">
  body{
    font-family: "Cambria";
    font-size: 18px;
    text-align: justify;
  }
  h1.title{
    text-align: center;
    font-size: 40px;
  }
  .author{
    text-align: center;
    font-size: 24px;
    font-family: "Cambria", "標楷體";
  }
</style>

```{r, warning = FALSE, message = FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      comment = "", 
                      dev.args = list(bg = 'lavender',                                       pointsize = 11))
library(magrittr)
library(stats)      # must load 'stats' before 'tidyverse' so that default 'filter()' function comes from 'tidyverse' 
library(tidyverse)
library(nycflights13)
options(dplyr.summarise.inform = FALSE)
temp = Sys.setlocale("LC_ALL","English.UTF-8")
library(xts)
library(tsibble)
library(lubridate)
library(skimr)
library(kableExtra)
ptable = function(df,digits = getOption("digits"),size = 14){
  df %>% knitr::kable(digits = digits) %>% 
    kable_classic(lightable_options = c("striped", "hover", "condensed"),
                  fixed_thead = list(enabled = T, 
                                     background = "lavender"),
                  font_size = size, full_width = F,
                  html_font = "helvetica")
}
```

```{r, include=FALSE}
options(width = 100)
local({
  hook_output <- knitr::knit_hooks$get('output')
  knitr::knit_hooks$set(output = function(x, options) {
    if (!is.null(options$max.height)) options$attr.output <- c(
      options$attr.output,
      sprintf('style="max-height: %s;"', options$max.height)
    )
    hook_output(x, options)
  })
})
```

### Question 1
```{r}
flights %>% transmute(across(ends_with("time") & -air_time,
                             ~ 60*as.integer(str_sub(.x, 1, -3))+as.integer(str_sub(.x, -2, -1)), .names = "new_{.col}"))
```
Explanation of the four variables in the output:

- new_dep_time: This variable is the transformed version of the original dep_time variable. It represents the scheduled departure time in minutes since midnight. The original dep_time variable was a string in the format "HH:MM:SS", and the new variable converts this to minutes by extracting the hour and minute values, converting them to integers, multiplying the hour value by 60, and adding the minute value.
- new_arr_time: This variable is the transformed version of the original arr_time variable. It represents the scheduled arrival time in minutes since midnight. The original arr_time variable was a string in the format "HH:MM:SS", and the new variable converts this to minutes using the same method as new_dep_time.
- new_sched_dep_time: This variable is the transformed version of the original sched_dep_time variable. It represents the scheduled departure time in minutes since midnight. The original sched_dep_time variable was a string in the format "HH:MM:SS", and the new variable converts this to minutes using the same method as new_dep_time.
- new_sched_arr_time: This variable is the transformed version of the original sched_arr_time variable. It represents the scheduled arrival time in minutes since midnight. The original sched_arr_time variable was a string in the format "HH:MM:SS", and the new variable converts this to minutes using the same method as new_dep_time.
```{r}
flights %>% 
  transmute(scheduled_air_time = air_time - dep_delay,
            actual_air_time = air_time - arr_delay)
```
### Question 2
```{r}
library(ggplot2)
library(gapminder)

# redefining 'dd'
dd = c('red','gray','yellow','cyan','white')
names(dd) = c('Africa','Americas','Asia','Europe','Oceania')

# filter data for selected years
gap_sely <- gapminder %>% filter(year %in% c(1952, 1977, 2002))

# create scatterplot with facets for each year and color by continent
ggplot(gap_sely, aes(x = log10(gdpPercap), y = lifeExp)) +
  geom_point(aes(color = continent), size = 2.5, alpha = 0.8) +
  scale_color_manual(values = dd) +
  xlim(c(2, 5)) +
  ylim(c(35, 85)) +
  facet_wrap(~ year, nrow = 1) +
  xlab("log10(GDP per capita)") +
  ylab("Life Expectancy")
```


