---
title: "Financial Big Data Quiz 4"
author: "108070014  陳品妤"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    number_sections: false
---

<style type = "text/css">
  body{
    font-family: "Cambria";
    font-size: 18px;
    text-align: justify;
  }
  h1.title{
    text-align: center;
    font-size: 40px;
  }
  .author{
    text-align: center;
    font-size: 24px;
    font-family: "Cambria", "標楷體";
  }
</style>

```{r, warning = FALSE, message = FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      comment = "", 
                      dev.args = list(bg = 'lavender',                                       pointsize = 11))
library(magrittr)
library(stats)      # must load 'stats' before 'tidyverse' so that default 'filter()' function comes from 'tidyverse' 
library(tidyverse)
library(nycflights13)
options(dplyr.summarise.inform = FALSE)
temp = Sys.setlocale("LC_ALL","English.UTF-8")
library(xts)
library(tsibble)
library(lubridate)
library(skimr)
library(kableExtra)
ptable = function(df,digits = getOption("digits"),size = 14){
  df %>% knitr::kable(digits = digits) %>% 
    kable_classic(lightable_options = c("striped", "hover", "condensed"),
                  fixed_thead = list(enabled = T, 
                                     background = "lavender"),
                  font_size = size, full_width = F,
                  html_font = "helvetica")
}
```

### Question 1
```{r}
flights %>% 
  group_by(carrier,zone = cut_number(distance, n = 6, labels = paste0("zone",1:6))) %>% 
  summarize(kpi = round(100*sum(is.na(dep_time))/n(),2)) %>% 
  group_by(zone) %>% 
  mutate(best_kpi = min(kpi), 
         best_carrier = carrier[kpi == best_kpi], 
         worst_kpi = max(kpi), 
         worst_carrier = carrier[kpi == worst_kpi]) %>% 
  distinct(zone, .keep_all = TRUE) %>% 
  select(zone, best_carrier, best_kpi, worst_carrier, worst_kpi)
```
The KPI in the above code is the percentage of flights with missing departure times ('dep_time') for each carrier and zone. The 'zone' is a variable created by dividing the 'distance' variable into 6 equal-sized groups using the `cut_number` function.

### Question 2
```{r}
flights %>% 
  group_by(carrier, zone = cut_number(distance, n = 6, labels = paste0("zone",1:6))) %>% 
  summarize(kpi = round(100 * sum(is.na(dep_time))/n(), 2)) %>% 
  ggplot() +
  geom_col(aes(x = zone, y = kpi, fill = carrier), position = "dodge") +
  facet_wrap(~ zone, scales = "free_x")
```
