---
title: "Financial Big Data HW 1"
author: "108070014  陳品妤"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    number_sections: false
---

<style type = "text/css">
  body{
    font-family: "Cambria";
    font-size: 18px;
  }
  h1.title{
    text-align: center;
    font-size: 40px;
  }
  .author{
    text-align: center;
    font-size: 24px;
    font-family: "Cambria", "標楷體";
  }
</style>

### Question 1
```{r}
library("weathermetrics")
data(airquality)
airquality$TempC <- fahrenheit.to.celsius(airquality$Temp)
str(airquality)
```
 ```{r echo = FALSE}
library("kableExtra")
airquality %>%
  kbl(caption = "Airquality") %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
   scroll_box(height = "300px")
```

### Question 2
```{r}
# install.packages("skimr")
library("skimr")
help("skimr")
```
Result of `skim()`:
```{r}
skim(airquality) %>%
  print(rule_width = 50)
```
Result of `summary()`:
```{r}
summary(airquality)
```

<br>

Difference between `skim()` & `summary()`:<br>
`skim()` provides summary statistics for more types of data than does `summary()`. `skim()` gives a broader overview of a data frame. 

### Question 3
* Mean
```{r}
apply(airquality, 2, mean, na.rm = F)
apply(airquality, 2, mean, na.rm = T)
```
* Median
```{r}
apply(airquality, 2, median, na.rm = F)
apply(airquality, 2, median, na.rm = T)
```
* Standard Deviation
```{r}
apply(airquality, 2, sd, na.rm = F)
apply(airquality, 2, sd, na.rm = T)
```
* Quantiles
`na.rm = F` cannot be used for quantiles.
```{r}
apply(airquality, 2, quantile, na.rm = T)
```
`na.rm = T` gets rid of invalid data, so those with `na.rm = F` may result in NAs.