---
title: "Financial Big Data HW 2"
author: "108070014  陳品妤"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    number_sections: false
---

<style type = "text/css">
  body{
    font-family: "Cambria";
    font-size: 18px;
    text-align: justify;
  }
  h1.title{
    text-align: center;
    font-size: 40px;
  }
  .author{
    text-align: center;
    font-size: 24px;
    font-family: "Cambria", "標楷體";
  }
</style>

```{r, include=FALSE}
options(width = 100)
local({
  hook_output <- knitr::knit_hooks$get('output')
  knitr::knit_hooks$set(output = function(x, options) {
    if (!is.null(options$max.height)) options$attr.output <- c(
      options$attr.output,
      sprintf('style="max-height: %s;"', options$max.height)
    )
    hook_output(x, options)
  })
})
```

```{r, warning = FALSE, message = FALSE, echo=FALSE}
library(psych)
library(Hmisc)
library(kableExtra)
library(skimr)
library(magrittr)
```

### Question 1
```{r max.height = '200px'}
market <- read.csv("marketing_data.csv")
str(market)
skim(market) %>%
  print(rule_width = 150)
```

### Question 2
```{r max.height = '200px'}
ls(market)
```

### Question 3
```{r}
sum(is.na(market))
```

### Question 4
```{r}
colSums(is.na(market))
```

### Question 5
```{r max.height = '200px'}
describe(market) %>% html()
summary(market, output.width = full)
```
The `describe()` function handles character variables by calculating the frequency and proportion of each distinct element. It also shows the missing, distinct, and total number of values. <br/>
The `summary()` function, on the other hand, handles character variables by specifying the length, class and mode.

### Question 6
```{r}
table(market$Education)
table(market$Marital_Status)
table(market$Country)
X <- list(market$Education, market$Marital_Status)
table(X)
```
The `table()` function creates a frequency table of categorical variables. Hence the first, second and third commands give the frequncy table of the columns 'Education', 'Marital_Status' and 'Country' respectively. It shows the number of times the distinct values are used in the columns.<br/>
The fourth command, with the use of the function `list()`, combines and gives the combined frequency tables the two columns 'Education' and 'Marital_Status'.<br/>

Using the %$% operator:
```{r}
market %$% table(Education)
market %$% table(Marital_Status)
market %$% table(Country)
market %$% table(X)
```

### Question 7
The 'Income' variable is not seen as a numeric variable because the original data set includes the dollar sign ($). We can fix this problem by removing the dollar signs via the following command.
```{r max.height = '200px'}
Modified_Income = gsub("\\$", "", market$Income)
Modified_Income
```

### Question 8
* Nunique
```{r max.height = '200px'}
Nunique <- apply(market, 2, n_unique)
Nunique
```
The `apply(X, MARGIN, FUN)` function returns a vector or array or list of values obtained by applying a function (specified by 'FUN') to margins (MARGIN = 1: row; MARGIN = 2: column) of a data frame (X). <br/>
In this case, `apply(market, 2, n_unique)` applies the function `n_unique()` to the columns in 'market'. <br/>
In addition, the `n_unique()` function calculates the number of unique elements excluding NAs.<br/> 
Hence, Nunique is the number of unique elements (excluding NAs) in each column.<br/>

* col
```{r max.height = '200px'}
col <- colnames(market)[Nunique == 2]
col
```
The `colnames()` function is generally used to change the names of columns. In this case however, it is used to select the names of the columns which number of unique elements excluding NAs (Nunique) equals to 2.<br/> This result is stored in 'col'.

* tbl
```{r max.height = '200px'}
tbl <- apply(market[,col], 2, table)
tbl
```
'tbl' stores the result of the `table()` function applied on the columns of the data frame 'market' with column names in 'col'. In other words, it shows the frequency table of the columns with 'Nunique' = 2.

* ratio
```{r max.height = '200px'}
ratio <- apply(market[,col], 2, mean)
ratio
```
'ratio' shows the mean of the columns with 'Nunique' = 2.

### Question 9
Definition of `myf()`:
```{r}
myf = function(var, byvar)
{
  by = unique(byvar)
  mout = NULL
  for(i in by){
    s = subset(var, byvar == i)
    m = colMeans(s)
    mout = cbind(mout, m)
  }
  colnames(mout) = by
  mout
}
```
Applying `myf()` to the 'market' data:
```{r}
varlist = c("MntWines", "MntSweetProducts", "MntMeatProducts", "MntFishProducts", "MntGoldProds")
colspec = c(4, 2, 1, 5, 8)
tbl = myf(subset(market, , varlist), market$Education)
tbl
```
Making a bar plot:
```{r}
barplot(tbl, beside = T, col = colspec)
legend("topright", inset = c(0,0), legend = varlist, col = colspec, pch = 16, cex = 1.1)
```
<br/><p style = "text-align: center;">------------ Redoing the above for the new variable 'agegrp' ------------</p><br/>
Defining 'agegrp':
```{r}
agegrp = ifelse(market$Year_Birth < 1960, "<1960",
              ifelse(market$Year_Birth < 1970, "[1960,1970)",
                  ifelse(market$Year_Birth < 1980, "[1970,1980)", ">=1980")))
```
The variable 'agegrp' classifies the data into four age groups according to the year of birth (<1960; 1960~1970; 1970~1980; >=1980).<br/>
Applying `table()`:
```{r}
age_tbl = table(agegrp)
age_tbl
```
Redefining `myf()` for 'agegrp':
```{r}
myf = function(var,agegrp)
{
  by = unique(agegrp)
  mout = NULL
  for(i in by){
    s = subset(var, agegrp == i)
    m = colMeans(s)
    mout = cbind(mout, m)
  }
  colnames(mout) = by
  mout
}
```
Applying `myf()`:
```{r}
varlist = c("Kidhome","Teenhome")
colspec = c(6, 7)
tbl = myf(subset(market, , varlist), market$Education)
tbl
```
The function `subset()` returns data frames that meet conditions. `subset(market, , varlist)` returns the subset of the columns 'Kidhome' and 'Teenhome'.<br/>
Since `myf()` cross compares the two specified variables, 'tbl' gives the result of the cross comparison between 'varlist' ('Kidhome' & 'Teenhome') and 'Education'.<br/>
Generating the barplot:
```{r}
barplot(tbl, beside = T, col = colspec)
legend("topright", inset = c(0,0), legend = varlist, col = colspec, pch = 16, cex = 1.1)
```
<br/>
The barplot shows the result of 'tbl' graphically with 'Kidhome' in the colour pink and 'Teenhome' in the colour yellow. The x and y-axis of the plot are 'Education' and frequncy values respectively.